### 2014-09-19 fundamentals/impl.tex
rough draft paragraphs on interchangability

\subsection{Agent Interchangability}
% interchangeability due to exchange behavior api

This approach enables ``apples-to-apples'' comparisons, something that has been 
sorely missing in previous simulators.

By making the facilities interchangeable, it combinatorically increases the 
number of scenarios that can be modeled. The user can choose to model just the 
front end or just the back end of a fuel cycle.

This is implemented with an API that focuses on treating the agents as black 
boxes.

>>>>

\subsection{Agent Interchangability}

A key compontent of the \Cyclus kernel architecture is the ability for
implementations of actors in a given simulation to be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be comparied to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle. Interchangability is accomplished by providing
APIs that define agent-to-agent interaction and agent-to-environment
interaction, primarily through the \Class{Agent} and \Class{Trader} interfaces.

The \Class{Agent} interface provides a notion of parent-child hierarchichal
relationship, where parents can choose to \textit{build} child agents and
\textit{decommission} child agents. The \Class{Trader} interface allows
agent-agent interaction through the trading of \Class{Resource}s. Usabe
archetypes in a \Cyclus simulation must implement the \Class{Agent} interface
and may optionally implement the \Class{Trader} interface. For example, a
\Class{Region} implements only the \Class{Agent} interface, whereas a
\Class{Facility} implements both the \Class{Agent} and \Class{Trader} interface,
allowing any \Class{Facility} to trade with another \Class{Facility}.
